Paper 1 Analysis

### 2015-10-21 Articles/Article_EcolEcon_2015/Paper1/Paper1-lambda-alpha.Rnw
Beginnings of a <<Fitted_Graph>>=

>>>>

<<Fitted_Graph, eval=FALSE>>=
fitted_and_resid_data %>% 
  filter(model=="CES") %>%
  gather()
  melt(measure.vars = c("iGDP", "fitted", "fittedExp"), 
       value.name = "value", variable.name = "variable") %>%
  mutate(label = paste(variable, energy)) %>%
  # Now collapse some of the information. Don't need multiple versions of the exponential model, e.g.
  filter(label %in% c("iGDP With energy", "fittedExp With energy", 
                      "fitted With energy", "fitted Without energy")
  ) %>% 
  mutate(
    label = plyr::mapvalues(label, 
                            from = c("iGDP With energy",  "fittedExp With energy",
                                     "fitted With energy", "fitted Without energy"), 
                            to = c("GDP",  "Ref. model",
                                   "w/ energy", "w/o energy")),
    label = relevelFactor(factor(label), 
                          c("GDP", "Ref. model", "w/o energy", "w/ energy"))
  ) %>%

  ggplot() +
  geom_line( mapping=aes(x=Year, y=value, group=label, linetype=label, size=label)) +
  scale_linetype_manual(values=c(1,2,4,3), name="") +
  scale_size_manual(name = "", values=c(1, 0.5, 0.5, 0.5)) +
  facet_grid(flavor ~ Country) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  scale_y_continuous(breaks=c(1, 2, 4, 6, 8, 10, 12)) +
  xlab("") +
  ylab("Indexed GDP (1960=1)") +
  xy_theme()

@
